\wt{5.1.3} Suppose that $A$ is a finite abelian group of order $n$ and that $n = p^{s_1}_{1} p^{s_2}_{2} \ldots p^{s_t}_{t}$. Let $A_{p_i}$ be the unique Sylow $p_i$-subgroup of $A$. Then $A \cong A_{p_1} \times A_{p_2} A_{p_1} \cdots A_{p_t};$ that is, $A$ is isomorphic to the direct product of its Sylow subgroups.
\wt{5.1.4} Let $A$ be an abelian group with $|A| = p^n$ for some prime $p$. Then $A$ is isomorphic to the direct product of cyclic subgroups of order $p^{e_1}, p^{e_2}, \ldots, p^{e_s}$ where $e_1 \ge e_2 \ge \cdots \ge e_s \ge 1$ and $e_1 + e_2 + \cdots + e_s = n$. This product is unique up to reordering the factors.
\wc{5.1.5 Fundamental Theorem of Finite Abelian Groups, I} Let $A$ be a finite abelian group. Then $A$ is a direct product of cyclic groups of prime power order. This product is unique up to reordering the factors.
\wt{5.1.6 Chinese Remainder Theorem} Let $m, n$ be nonzero coprime integers. Then $C_{mn} \cong C_m \times C_n$. 
\wpf{} Let the generator of $C_m$ be $a$ and let the generator of $C_n$ be $b$. Define group homomorphism $\phi : \mathbb{Z} \to C_m \times C_n$, $r \mapsto (a^r, b^r)$. Then $\ker\phi = \{r \in \mathbb{Z} : r \in m\mathbb{Z} \text{ and } r \in n\mathbb{Z}\} = m\mathbb{Z} \cap n\mathbb{Z} = \ell \mathbb{Z}$ where $\ell = \mathrm{lcm}(m,n)$. Since $m,n$ are coprime, $\ell = mn$. By 1st iso. thm. $\im\phi \cong \mathbb{Z}/mn\mathbb{Z} \cong C_{mn}$. Thus $|\im\phi| = mn$ and $\im\phi = C_m \times C_n$.
\wc{5.1.8 Fundamental Theorem of Finite Abelian Groups, II} Any finite abelian group of order $n$ can be written as a direct product of cyclic groups $C_{n_1} \times C_{n_2} \times \cdots \times C_{n_s}$ where $n_i$ divides $n_{i+1}$ for each $i = 1,2,\ldots,s-1$, and $n_1n_2\ldots n_s = n$.
\wde{5.1.9 Exponent}  The \textit{exponent}, $e(G)$, of a finite group is the least common multiple of the orders of the elements of $G$. 
\wl{5.1.11} Let $A$ be a finite abelian group. then $A$ contains an element of order $e(A)$.
\wc{5.1.12} If $a$ is a finite abelian group with $e(A) = |A|$ then $A$ is cyclic.
\wt{5.1.13} Let $A$ be a finite subgroup of the multiplicative group $K^* := K \setminus \{0\}$ of a field $K$. Then $A$ is a cyclic group.
\wc{5.1.14} The multiplicative group of nonzero elements of a finite field is cyclic.